Voice Classification by Neural Networks

### 2015-05-18 paper.tex
ROC section basically finished

As we vary the threshold, the neural net's position in ROC space will vary.
As the threshold moves from 0 to 1, the neural net will trace out a curve in ROC space (see \cref{fig:rocexample}, which we will call the model's \emph{ROC curve}.
% ROC curve intuition

\begin{figure}
\centering
% \includegraphics{aux/rocexample.pdf}
\caption{An example ROC curve.}
\label{fig:rocexample}
\end{figure}
% TODO include

% ROC space (false pos, true pos)
% ROC curve
% AUC
% insert figure

>>>>

As we vary the threshold, the neural net's position in ROC space will vary.
In particular, as we vary threshold from 0 to 1, the neural net will trace out a curve in ROC space (see \cref{fig:rocexample}), which we will call the model's \emph{ROC curve}.
Note that a random classifier, with no distinguishing power between positive and negative instances, would have an ROC curve coinciding with the line $y = x$, as we expect equal true and false positive rates from this classifier.
On the other hand, a model whose ROC curve lies above this line would tend to give higher ``scores" (the continuous output) to positive instances than to negative ones.
Thus, we would like our model's ROC curve to lie as far above the line $y = x$ as possible.

This intuition suggests that a good metric for evaluating our models could be the area under the ROC curve.
Indeed, \emph{Area Under Curve} (AUC) is a common metric for binary classification.
Its value can range from 0 to 1, though in practice, our values will lie in $(0.5, 1)$.
A value of 0.5 corresponds to a model no better than a random classifier, while a value of 1 corresponds to a model that perfectly distinguishes between positive and negative instances.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{aux/rocexample.pdf}
\caption{An example ROC curve, with AUC $\approx 0.7804$. The dashed line shows $y = x$.}
\label{fig:rocexample}
\end{figure}
